Extrinsic Type Inference (DRAFT 2025-06-08)

### 2025-07-08 extrinsic_type_inference_paper/paper.tex
update

\noindent
Proof subtyping substance states that the generated constraints are satisfiable
assuming the contextual constraints are satisfiable, with respect
to all interpretations of the contextual skolems.   
The proof is by following a slightly stronger statement,
which says that the generated constraints are satisfiable, and 
that the constraints on a single variable are as strong or stronger
than all the constraints with respect to that variable.
The proof of the stronger statement is by induction.
The only cases that are actually interesting are the variable rules
where new constraints are generated.
In every case that a new constraint is added, it is a constraint on
a single variable, and in each case the solver compares the new bound on the variable
to the previous bounds on the other side of the variable. Since bounds on
opposite sides are the only opportunities for contradictions, the requirement
preserves the strengthened substance property from the induction hypothesis.

>>>>

\noindent
Proof subtyping substance states that the generated constraints are satisfiable
assuming the contextual constraints are satisfiable, with respect
to all interpretations of the contextual skolems.   
This property follows directly from a slightly stronger theorem,
which states that the generated constraints are satisfiable and 
that the constraints on a single variable are as strong or stronger
than all the constraints with respect to that variable.
The proof of the stronger statement is by induction.
The only cases that are actually interesting are the variable rules
where new constraints are generated.
In every case that a new constraint is added, it is a constraint on
a single variable, and in each case the solver compares the new bound on the variable
to the previous bounds on the other side of the variable. Since bounds on
opposite sides are the only opportunities for contradictions, the requirement
preserves the strengthened substance property from the induction hypothesis.
